Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-09-26 paper/PaperTRA/PaperTRA.Rmd
Not just metro areas
Update abstract

abstract: | 
  In metropolitan areas, car trips can be replaced by a combination of public transit and cycling for the first-and-last mile. This paper estimates the potential for cycling + public transit (PT) as a substitute for car trips in the Lisbon metropolitan area and assesses its socio-environmental impacts using open data and open source tools.
  A decision support tool that facilitates the design and development of a metropolitan cycling network was developed (_biclaR_). A scenario of intermodality introduced, and its socio-environmental impacts were assessed using the _HEAT for Cycling_ and the _HEAT as a Service_ tools. The impacts of shifting car trips to PT were also estimated and monetized.
  The results indicate that 20% of the current trips can be made with the bicycle + PT combination. Shifting to cycling for the first-and-last mile can reduce annual CO~2~eq emissions from 6,000 tons/day, and the 10-year socio-environmental benefits account from €230 million. For the PT leg, the transfer from car avoids of at least 8,500 tons of CO~2~eq emissions per year.
  The information on socio-economic benefits can support policymakers in prioritizing interventions to reduce the reliance on individual motorized transportation and effectively communicate their decisions.
keywords: 
  - Active transport
  - Intermodality
  - First and last mile
  - Health economic assessment
  - Environmental impacts
  - Open data and methods
bibliography: bibliography.bib
# Use csl when using default citation_package for Pandoc citeproc
csl: https://www.zotero.org/styles/springer-lecture-notes-in-computer-science
# citations with arabic numbers is prefered when using natbib
natbiboptions: numbers

>>>>

abstract: | 
  A high proportion of car trips can be replaced by a combination of public transit and cycling for the first-and-last mile. This paper estimates the potential for cycling combined with public transit (PT) as a substitute for car trips in the Lisbon metropolitan area and assesses its socio-environmental impacts using open data and open source tools.
  A decision support tool that facilitates the design and development of a metropolitan cycling network was developed (_biclaR_). The social and environmental impacts were assessed using the _HEAT for Cycling_ and the _HEAT as a Service_ tools. The impacts of shifting car trips to PT were also estimated and monetized.
  The results indicate that 20% of cart trips could switch to the bicycle + PT combination. Shifting to cycling for the first-and-last mile stages can reduce annual CO~2~eq emissions from 6,000 tons/day, with benefits over 10 years of €230 million. For the PT leg, the transfer from car avoids of at least 8,500 tons of CO~2~eq emissions per year.
  This evidence can support policymakers to prioritize interventions that reduce the reliance on private motor vehicles.
keywords: 
  - Active transport
  - Intermodality
  - First and last mile
  - Health economic assessment
  - Environmental impacts
  - Open data and methods
bibliography: bibliography.bib
# Use csl when using default citation_package for Pandoc citeproc
csl: https://www.zotero.org/styles/springer-lecture-notes-in-computer-science
# citations with arabic numbers is prefered when using natbib
natbiboptions: numbers
